Technical Report

### 2018-06-18 fully-abstract-comp/technical-report.tex
removed ms_code from reasonability

\dominique{The below is an experimental reformulation of the reasonability requirement for the FTLR and full abstraction formulation.  All remarks welcome..
  The main change is that it now says that after a call, the post-return code is also expected to behave reasonably under reasonable assumptions. 
}
\dominique{TODO: better name than ``reasonable'' for all of this.}
Take a block of code memory $\mscode$, a set of trusted addresses $\ta$ and sets of return pointer and closure seals $\gsigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ if $n=0$
or the following implications hold.
\begin{itemize}
\item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \neq 0$ and $\gsigrets \neq \emptyset$, then $[\baddr,\eaddr] \# \dom(\mscode)$
\item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\gsigrets\cup \gsigcloss)$ then $\vsc$ is reasonable up to $n - 1$ steps.
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
\end{itemize}

@@

  \item $\Phi.\ms_\stk$ is reasonable up to $n-1$ steps in memory $\Phi.\mem$ for all $a$
    TODO
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
    This follows from $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$.
  \end{itemize}
\end{proof}

>>>>

\dominique{The below is an experimental reformulation of the reasonability requirement for the FTLR and full abstraction formulation.  All remarks welcome..
  The main change is that it now says that after a call, the post-return code is also expected to behave reasonably under reasonable assumptions. 
}
\dominique{TODO: better name than ``reasonable'' for all of this.}
Take a set of trusted addresses $\ta$ and sets of return pointer and closure seals $\gsigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ if $n=0$
or the following implications hold.
\begin{itemize}
\item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \neq 0$ and $\gsigrets \neq \emptyset$, then $[\baddr,\eaddr] \# \dom(\ta)$
\item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\gsigrets\cup \gsigcloss)$ then $\vsc$ is reasonable up to $n - 1$ steps.
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
\end{itemize}

@@

  \item $\Phi.\ms_\stk$ is reasonable up to $n-1$ steps in memory $\Phi.\mem$ for all $a$:

    TODO
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint:

    This follows from $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$.
  \end{itemize}
\end{proof}
